---
title: "New Stuff"
author: "Alan"
date: "March 27, 2014"
output:
  beamer_presentation:
    keep_tex: yes
    theme: Madrid
  ioslides_presentation: default
  revealjs_presentation: default
incremental: yes
---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see [http://rmarkdown.rstudio.com.](http://rmarkdown.rstudio.com)

\pause

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

>- Bullet 1 --- say something
>- Bullet 2 --- baffle us with more
>- Bullet 3 --- you talk too much


By the way, see \eqref{CDF}

## Slide with R Code and Output

```{r, comment = NA}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars, col = "red", pch = 19)
```



## Some Mathematics?

\LaTeX is so cool ...

\begin{equation}\label{CDF}
F(x) = \int_{-\infty}^{x}f(x)\,dx
\end{equation}

\textbf{Now, we use the \LaTeX{} environment \texttt{enumerate}.}

\begin{enumerate}
\item Say something
\pause
\item Say some more
\pause
\item Shut up...you said too much
\end{enumerate}

## Mathematics and Inline Expressions

This really rocks!  Suppose we want to compute

$$\int_{1}^{1.5}\frac{2}{x^2}\,dx$$

\pause

```{r label = INTEGRAL, echo = TRUE, comment = NA}
f <- function(x){2/x^2}
ans <- integrate(f, 1, 1.5)$value
ans
```

\pause

$$\int_{1}^{1.5}\frac{2}{x^2}\,dx = `r ans`$$

## \texttt{ggplot2} Graphs

```{r echo = FALSE, comment = NA, message = FALSE, fig.height = 5}
library(ggplot2)
library(PASWR2)
ggplot(data= VIT2005, aes( x= totalprice)) + geom_density(fill = "lightblue", alpha = .3) + theme_bw()
```